More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-01-23 2016-Weak-FH-Bisim/WeakBisim.tex

By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1 and 2 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}

\TODO{We will add side conditions ?? }\\

Concerning $Q$, we consider only the paths for which it moves. So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$.

Therefore, we will obtain:

$\forall p \in [0\ldots n_1] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
and
$ Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0\ldots n_2] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\
such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
\TODO{We will discuss}

For each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$ in the form:
\begin{mathpar}
Q\models{\openrule
			{
				(\beta_p)_j^{J_p}, {\Pred_p},  
				{\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]

\end{mathpar}
By rule (\WTTrois)  we can conclude that  we have:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
such that $\gamma_p = \vis{\beta_p}$.
\TODO{maybe it is better to use $\gamma_p=[\beta_p]$}\\

>>>>

By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}

$s_l=s_{0l} \wedge s_{{m_1}l}=t_l \wedge t'_l = u_{0l} \wedge s'_l=s_{{m_2}l}$
\TODO{Avant d'ajouter la suite, il faudrait se mettre d'accord sur les notations}\\

Concerning $Q$, we consider only the paths for which it moves. So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$. We also consider for the third case $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$. So we have: \\ 
$\forall p \in [0\ldots n_1] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
and
$ Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
				{\Post}\,''}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0\ldots n_2] Q\models{\openrule
			{
				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
				{{\Post_p}\!\!''}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\

such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\

Let us consider the first item, in the series of $(n_1+1)$  actions $\alpha_p$ some of them may be non-observable ($\tau$ transition). By considering $\tau$  actions we split the sequence of $n_1+1$ actions into subsequences, such that each subsequence is a series of  $\tau$ transitions  ending by not more than one observable transition. For each subsequence we can write the  following:\\
$Q\models{\openrule
			{
				(\beta_{i})_j^{j\in J\cap\Holes(Q)}, {{\Pred_i}\!\!''},  
				{{\Post_i}\!\!''}}
				{\ostate{s_{il}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{s_{(i+1)l}^{l\in L_Q}}}
				}%\]
, Q\models{\openrule
			{
				(\beta_{(i+1)})_j^{j\in J\cap\Holes(Q)}, {{\Pred''_{(i+1)}}},  
				{{\Post''_{(i+1)}}}}
				{\ostate{s_{(i+1)l}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{s_{(i+2)l}^{l\in L_Q}}}
				}%\]
\ldots\\
Q\models{\openrule
			{
				(\beta_{k})_j^{j\in J\cap\Holes(Q)}, {{\Pred_k}\!\!''},  
				{{\Post_j}\!\!''}}
				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\alpha_k}
				\ostate{s_{(k+1)l}^{l\in L_Q}}}
				}%\]
$\hspace{0.5cm}
where $1\leq i<n_1$ and $i<k$.\\
By Lemma \ref{lem-rel-OT-WOT} we obtain the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{j\in J\cap\Holes(Q)}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}

where $s_{il} = s_{pl}$ and $s_{(p+1)l}=s_{(k+1)l}$ 
\TODO{et le reste}

Particular attention should be paid to the last subsequence which may not end by an observable action. We proceed in the same way we obtain an non-observable weak open transition; and by applying  rule (\WTTrois) to the resulting non-observable weak open transition and the previous weak open transition we obtain a weak open transition.

By iterating this reasoning over the states $u$ and $t$  one have that: for each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (n_1\!+\!n_2)\!+\!1]$ in the form and $\alpha_p \neq \tau$:
\begin{mathpar}
Q\models{\openrule
			{
				(\beta_p)_j^{J_p}, {\Pred_p},  
				{\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]

\end{mathpar}
We can conclude that we have a $\symb{WOT}_p$:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
such that $\gamma_p = \vis{\beta_p}$.
\TODO{le reste une fois mis d'accord sur la notation}\\

In this case, the number of weak open transitions
might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.

\TODO{I STOPPED THERE!!!}
